Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework

### 2019-04-15 paper/main.tex
Alter abstract

Precoding matrices obtained via SVD\footnote{Singular Value Decomposition} of the MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions. 
However, a key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
Considering the limited bit budget for such CSI\footnote{Channel State Information} feedback, the precoders need to be quantized with single digit number of bits.
For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
This odious task is helped by the presence of an underlying manifold structure, and temporal/frequency correlations in the precoders. 
In this work, we introduce a reservoir computing framework for the task of prediction of new precoders upon observation of past such precoders, by utilizing temporal correlations. 
This is a departure from existing methods which exploit the non linear geometry endowed by the manifold structure to perform the same.
Alternately, the non-linear relation is captured in our work via the dynamical reservoir state via the training process of the reservoir. 
Simulations reveal reduced quantization error, which results in lower BER as well as improved achievable rate, as compared to previous work.

>>>>

Precoding matrices obtained from the SVD of the wireless MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions. 
However, a key step that enables this improved performance is feedback of these precoders to the transmitter from the receiver.
Since bit budget for such channel state information (CSI) feedback is limited, precoders need to be quantized effectively using with very few bits.
For a $N_T \times N_R$ MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
This can be simplified by using the underlying manifold structure, and temporal/frequency correlations in the precoders. 
In this work, we introduce a reservoir computing based framework for prediction of the new precoders by observing pastprecoders and utilizing temporal correlations. 
Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder interpolation and prediction.
Here, this non-linear relationship is captured using the dynamical reservoir state as part of the training process of the reservoir. 
Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
